---
title: "Lab09"
author: "Haoran Zhang"
date: "2021/10/29"
output: 
  html_document: 
    keep_md: yes
---
## Question 1: Think
Parallel computing may be used in weather forecast, partial differential equations and astrophysics.

## Question 2: Before you
The following functions can be written to be more efficient without using parallel:
1. This function generates a n x k dataset with all its entries distributed poission with mean lambda.
```{r}
fun1 <- function(n = 100, k = 4, lambda = 4) {
  x <- NULL
  for (i in 1:n)
    x <- rbind(x, rpois(k, lambda))
  return(x)
}
fun1(5,10)
```

```{r}
fun1alt <- function(n = 100, k = 4, lambda = 4) {
  matrix(rpois(n*k, lambda),nrow = n, ncol = k)
}


# Benchmarking
microbenchmark::microbenchmark(
  fun1(n=1000),
  fun1alt(n=1000), unit="relative"
)
```

## Question 3: Find the column max (hint: Checkout the function max.col()).
```{r}
# Data Generating Process (10 x 10,000 matrix)
set.seed(1234)
x <- matrix(rnorm(1e4), nrow=10)

# Find each column's max value
fun2 <- function(x) {
  apply(x, 2, max)
}

fun2alt <- function(x) {
  # Position of the max value per row of x.
  idx<-max.col(t(x))
  # Do something to get the actual max value
  # x[cbindc(1,15)]-x[1,15]
  # Want to access x[1,16],x[4,1]
  # x[rbind(c(1,16),c(4,1))]
  # Want to access x[4,16],x[4,1]
  # x[rbind(4,c(16,1))]
  x[cbind(idx, 1:ncol(x))]
}

all(fun2(x)==fun2alt(x))
# Benchmarking
microbenchmark::microbenchmark(
  fun2(x),
  fun2alt(x),unit = "relative"
)
```

Example of the max.col function... what just happened?

```{r}
set.seed(42343)
M <- matrix(runif(12), ncol = 4)
M # How does it look?
fun2(M)
t(M) # Transpose M...
idx <- max.col(t(M)) # Then the max.col
# c(3, 1, 3, 1)
idx
# How do the coordinates look like?
cbind(idx, 1:ncol(M))
# The final result
M[cbind(idx, 1:ncol(M))]
```

## Question 4: Bootstrap

```{r}
library(parallel)
my_boot <- function(dat, stat, R, ncpus = 1L) {
  
  # Getting the random indices
  n <- nrow(dat)
  idx <- matrix(sample.int(n, n*R, TRUE), nrow=n, ncol=R)
 
  # Making the cluster using `ncpus`
  # STEP 1: GOES HERE
  cl <- makePSOCKcluster(ncpus)
  
  # STEP 2: GOES HERE
  clusterSetRNGStream(cl, 123) # Equivalent to `set.seed(123)`
  clusterExport(cl, c("stat", "dat", "idx"), envir = environment())
  
  # STEP 3: THIS FUNCTION NEEDS TO BE REPLACES WITH parLapply
  ans <- parLapply(cl = cl, seq_len(R), function(i) {
    stat(dat[idx[,i], , drop=FALSE])
  })
  
  # Coercing the list into a matrix
  ans <- do.call(rbind, ans)
  
  # STEP 4: GOES HERE
  stopCluster(cl)
  
  ans
  
}
# Bootstrap of an OLS
my_stat <- function(d) coef(lm(y ~ x, data=d))
# DATA SIM
set.seed(1)
n <- 500; R <- 5e3
x <- cbind(rnorm(n)); y <- x*5 + rnorm(n)
# Checking if we get something similar as lm
ans0 <- confint(lm(y~x))
ans1 <- my_boot(dat = data.frame(x, y), my_stat, R = R, ncpus = 2L)
# You should get something like this
t(apply(ans1, 2, quantile, c(.025,.975)))
```

Is it faster?

```{r}
system.time(my_boot(dat = data.frame(x, y), my_stat, R = 4000, ncpus = 1L))
system.time(my_boot(dat = data.frame(x, y), my_stat, R = 4000, ncpus = 2L))
```